### 2021-04-11 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsection{Independent Leakages}
If A and B are independent leakages, the total information leakage will be:
$$L_{\mathit{total}} = L_A + L_B $$

@@

\begin{figure}[h]
  \begin{minipage}{0.45\linewidth}
      \begin{tabular}{rrrr}
        \toprule
        & $a$ & $\lnot a$  & total\\
        \midrule
        $b$   & 255 (255.5) & 253 (252.5) &   508  \\
        $\lnot b$   & 260 (259.5)  & 256 (256.5) &    516   \\
        total &   515 &  509   & 1,024   \\
        \bottomrule
      \end{tabular}%
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\linewidth}
      \begin{tabular}{rrrr}
        \toprule
        & $c$ & $\lnot c$  & total\\
        \midrule
        $d$   & 809 (764.8) & 82 (126.2) & 891    \\
        $\lnot d$   & 70 (114.2)  & 63 (18.8)&  133     \\
        total &  879 &  145  & 1,024    \\
        \bottomrule
      \end{tabular}%
  \end{minipage}
  \caption{The Contingency Table for the experiments. The numbers in the bracket are expected values. }\label{chapter5:fig:con_table}
\end{figure}

\section{Design}
In this section, we explain the implementation of \ctool{}.
we first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.

>>>>

\subsection{Independent Leakages}
If A and B are independent leakages, the total information leakage will be:
\[L_{\mathit{total}} = L_A + L_B \]

@@

\begin{figure}[h]
  \begin{minipage}{0.40\linewidth}
      \begin{tabular}{rrrr}
        \toprule
        & $a$ & $\lnot a$  & total\\
        \midrule
        $b$   & 255 (255.5) & 253 (252.5) &   508  \\
        $\lnot b$   & 260 (259.5)  & 256 (256.5) &    516   \\
        total &   515 &  509   & 1,024   \\
        \bottomrule
      \end{tabular}\caption*{(a)}
  \end{minipage}
\hspace{-15pt}
\hfill
\hspace{-15pt}
  \begin{minipage}{0.40\linewidth}
      \begin{tabular}{rrrr}
        \toprule
        & $c$ & $\lnot c$  & total\\
        \midrule
        $d$   & 809 (764.8) & 82 (126.2) & 891    \\
        $\lnot d$   & 70 (114.2)  & 63 (18.8)&  133     \\
        total &  879 &  145  & 1,024    \\
        \bottomrule
      \end{tabular}\caption*{(b)}
  \end{minipage}
  \caption{The contingency table for the experiments. The numbers in the bracket are expected values. }\label{chapter5:fig:con_table}
\end{figure}

Assume we generate $1024$ random inputs and record the memory access each time. For the example in Figure~\ref{chapter5:fig:multiple}, we use $a$ to denote the function \textsf{a} executes and $\lnot a$ to denote the function \textsf{a} does not execute during the execution. After we calculate the number of the same observation, we get the contingency table shown in Figure~\ref{chapter5:fig:con_table}.
\section{Design}
In this section, we explain the implementation of \ctool{}.
we first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.
